\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tabularx}

\setmainfont{Latin Modern Roman}
\setsansfont{Latin Modern Sans}
\setmonofont{Latin Modern Mono}

\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{lightgray}{RGB}{128,128,128}

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue
}

\titleformat{\section}{\Large\bfseries\sffamily\color{darkblue}}{}{0em}{}
\titleformat{\subsection}{\large\bfseries\sffamily}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{}{0em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\pagestyle{empty}

\begin{document}

% Header
\begin{center}
{\Huge\bfseries\sffamily\color{darkblue} MARKUS SCHULTE}\\[0.3em]
{\Large\sffamily Anti-CV: A Professional Collection of Spectacular Failures}\\[0.5em]
{\large\sffamily Cloud Architect \& Software Engineer | Cologne, Germany}\\[0.3em]
\href{mailto:mail@schulte-development.de}{mail@schulte-development.de} | +49 178 7217768 | \href{https://schulte-development.de}{schulte-development.de}
\end{center}

\vspace{0.5em}

% Professional Anti-Summary
\section{Professional Anti-Summary}

After 18+ years of making gloriously educational mistakes in software development, I've perfected the art of learning things the hard way. My specialty lies in discovering what doesn't work before stumbling upon what does, often while leading teams through the same delightful journey of discovery.

\textbf{My Superpower:} Turning expensive lessons into valuable experience, one failure at a time.

\textbf{Career Motto:} "If you're not failing, you're not trying hard enough... or you're not being honest about it."

% Key Failures Overview
\section{Signature Failures \& Hard-Won Lessons}

\begin{itemize}[leftmargin=1em, itemsep=0.3em]
\item \textbf{Leadership Reality Check:} Became Head of Development at age 24 without management experience. Learned that technical skills don't automatically translate to people skills (who knew?).
\item \textbf{Technology Prophet Syndrome:} Consistently picked familiar technologies over innovative ones. Chose Sphinx over ElasticSearch because it seemed "less exotic" – watched team migrate to ElasticSearch later.
\item \textbf{Kubernetes Skepticism:} Refused to embrace the "orchestration revolution," insisting it was too complex. Still maintain this unpopular opinion, much to the horror of DevOps enthusiasts.
\item \textbf{Microservices Disillusionment:} Discovered that real-world microservices are nothing like the conference talks. Simple changes became multi-service nightmares.
\item \textbf{Academic Procrastination:} Turned a 5-year degree into 8 years by working full-time. Proved that parallel processing doesn't work for humans.
\item \textbf{Solo Developer Syndrome:} Voluntarily took on projects where I was the only developer. Learned that "job security" and "no backup" are terrifyingly synonymous.
\end{itemize}

\section{Recent Professional Disasters}

\subsection{November 2024 — Present: Cloud Architect at LBBW}
\textbf{Current Failure in Progress:} Attempting to modernize a major German bank's IT infrastructure with 80+ people involved. Because if you're going to fail, fail spectacularly with maximum witnesses.

\textbf{Key Challenges I'm Struggling With:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item Managing architectural responsibility for 10 applications while the "Skywalker" platform remains production-unused
\item Evaluating cloud platforms that may never see real workloads
\item Creating migration templates for hundreds of legacy applications (because catalogs are fun)
\item Maintaining enthusiasm for Azure Calculator cost projections that may never materialize
\end{itemize}

\subsection{October 2021 — December 2024: Cloud Architect at Union Investment}
\textbf{The Three-Year Learning Marathon:} What started as a simple platform modernization became a masterclass in why enterprise transformations take forever.

\textbf{Spectacular Learning Opportunities:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Scope Creep Champion:} Turned a simple website refresh into a complete SCS architecture overhaul. Because why solve one problem when you can solve eight?
\item \textbf{Over-Engineering Olympic Gold:} Built a microfrontend toolkit for 80,000 users. Created event-driven architecture for search that could handle millions but serves thousands.
\item \textbf{Technology Evangelism:} Convinced teams to adopt Web Components and Self-contained Systems. Spent 50\% of time explaining why this was better than their existing solution.
\item \textbf{Team Leadership Learning Curve:} Managed 5-7 developers while serving as Product Owner. Discovered that "technical expertise" and "knowing what to build" are completely different skills.
\item \textbf{The Great Search Odyssey:} Spent 18 months building unified search across distributed systems. Learned that "unified" and "distributed" are mutually exclusive concepts.
\end{itemize}

\textbf{360° Feedback Reality Check:} Consistently rated high on technical skills, consistently reminded to "consider pace of explanations for less technical stakeholders." Translation: I talk too fast about complex things.

\subsection{December 2021 — November 2024: Middleware Engineer at Saloodo!}
\textbf{The Solo Developer's Dilemma:} Accepted a part-time role alongside Union Investment because I thought juggling two jobs would be "efficient."

\textbf{Lessons in Overcommitment:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Multi-tasking Myth:} Managed two demanding projects simultaneously. Discovered that "part-time" in enterprise environments is a theoretical concept.
\item \textbf{Solo Ownership Anxiety:} Became the only person who understood critical middleware serving 10M+ records. Learned that "bus factor of 1" is not a feature.
\item \textbf{Database Wrestling:} Fought with Saloodo's inconsistent database schema containing malformed JSON and incorrect types. Spent more time on error handling than business logic.
\item \textbf{Perfect Uptime Pressure:} Achieved 100\% uptime for 3 years. The stress of being the only person who could fix it when it broke was... character-building.
\end{itemize}

\section{Earlier Career Disasters}

\subsection{2016 — 2019: The Freelancing Reality Check}
\textbf{Trusted Shops (2018-2019):} Encountered my first real microservices architecture. Learned that conference talks about microservices skip the part where simple changes require touching 47 different services.

\textbf{toom Baumarkt (2016-2017):} First encounter with Kubernetes. Decided it was "too complex for simple applications." Still maintain this unpopular opinion, much to everyone's dismay.

\textbf{Key Failures:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Kubernetes Rejection:} Refused to embrace the orchestration revolution. Insisted it was overkill for most applications. Remain stubbornly convinced this was correct.
\item \textbf{Microservices Disillusionment:} Discovered that real microservices are nothing like the marketing materials. Simple changes became multi-team negotiations.
\item \textbf{Technology Consulting Challenges:} Learned that being technically correct doesn't automatically make your recommendations popular or adopted.
\end{itemize}

\subsection{2016 — 2023: Atlassian Marketplace Entrepreneur}
\textbf{The Accidental Business Owner:} Created Bamboo add-ons that somehow made money for 7 years. Learned that maintaining legacy Java plugins is not as glamorous as it sounds.

\textbf{Entrepreneurial Education:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Market Timing Luck:} Succeeded purely by being first to market, not by business acumen
\item \textbf{Support Nightmare:} Discovered that 83 customers across 15 countries all have different interpretations of "simple" requirements
\item \textbf{Technical Debt Accumulation:} Maintained 7-year-old Java code that worked but nobody (including me) wanted to touch
\end{itemize}

\subsection{2007 — 2014: The werkenntwen Experience}
\textbf{The Leadership Experiment:} Became Head of Development at 24 because I could code. Learned that management and programming are completely different skill sets.

\textbf{Epic Learning Opportunities:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Premature Promotion:} Accepted Head of Development role without management experience. Thought "how hard could it be?" Spoiler: Very hard.
\item \textbf{Technology Conservatism:} Chose Sphinx over ElasticSearch because it seemed "less risky." Watched team migrate to ElasticSearch after I stepped down.
\item \textbf{Leadership Style Discovery:} Started with micromanagement, evolved to laissez-faire. Learned that finding your management style requires experimenting on real people.
\item \textbf{Scale Challenges:} Managed platform for 9M+ users while learning management on the job. Somehow survived with platform intact.
\end{itemize}

\section{Personal Projects (AKA Side Quest Failures)}

\subsection{2025: AI-Powered CV Generation}
Currently building automated CV generation using Claude AI. Because manually updating CVs is so 2024. Ironically, this anti-CV is manually written.

\subsection{2018: Jenkins ↔ GitHub Integration}
Built elaborate integration system that worked perfectly... for exactly zero users. Learned that "cool technology" and "market need" are unrelated concepts.

\subsection{2015: Cryptocurrency Trading Bot}
Created Bitcoin arbitrage algorithms during the first crypto boom. Perfectly timed to enter the market just before a major crash. Learned that "algorithmic trading" and "getting rich quick" are different things.

\section{Educational Failures}

\subsection{2004 — 2012: The Extended University Experience}
\textbf{University of Koblenz-Landau — Computer Science Diploma}

\textbf{Key Academic Failures:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item \textbf{Time Management Disaster:} Turned 5-year degree into 8-year odyssey by working full-time. Proved that humans can't actually parallel process.
\item \textbf{Priority Confusion:} Chose immediate income over focused study. Learned that "practical experience" and "academic progress" compete for the same 24 hours.
\item \textbf{Overconfidence in Multi-tasking:} Believed I could maintain full-time work and full-time study. Mathematics proved otherwise.
\end{itemize}

\textbf{Redeeming Factor:} Graduated with distinction (magna cum laude), proving that taking longer sometimes works out.

\subsection{2003: High School — The Foundation}
\textbf{Gymnasium Haren (Ems) — Abitur}

Early technology disasters included teaching myself PHP from a reference book and creating forums for friends. Discovered that "it works on my machine" is not a deployment strategy.

\section{Current Skill Gaps \& Ongoing Failures}

\begin{multicols}{2}
\textbf{Technologies I Avoid:}
\begin{itemize}[leftmargin=1em, itemsep=0.1em]
\item Kubernetes (too complex)
\item NoSQL databases (prefer structure)
\item Microservices (scarred by experience)
\item Frontend frameworks (changes too fast)
\item AI/ML (still learning)
\end{itemize}

\textbf{Skills I'm Failing to Develop:}
\begin{itemize}[leftmargin=1em, itemsep=0.1em]
\item Executive communication
\item Sales \& business development
\item Team scaling beyond 9 people
\item Strategic planning (beyond 3 years)
\item Public speaking confidence
\end{itemize}
\end{multicols}

\section{Career Breaks (AKA Strategic Retreats)}

\textbf{April 2020 — September 2021:} Parental leave during COVID-19. Perfect timing to exit the market just as remote work became standard.

\textbf{August 2015 — December 2015:} Extended travel break. Learned that "finding yourself" is expensive and doesn't improve your LinkedIn profile.

\textbf{2003 — 2004:} Mandatory military service. Learned that following orders is a skill I don't possess naturally.

\section{References \& Testimonials}

\textbf{What People Actually Say:}
\begin{itemize}[leftmargin=1em, itemsep=0.2em]
\item "Consider pace of explanations for less technical stakeholders" — Every 360° feedback ever
\item "Brings exactly what we need" — Union Investment (right after explaining why their current approach was wrong)
\item "Makes work enjoyable and professional" — Team member (translation: makes jokes during stressful moments)
\item "Ability to analyze complex architectures" — Colleague (translation: enjoys making simple things complicated)
\end{itemize}

\vspace{1em}
\begin{center}
\textcolor{lightgray}{\footnotesize This anti-CV was compiled using AI assistance, because even failure documentation can be optimized.}
\end{center}

\end{document}